---
title: "ASD Prevalance based on Study Design"
output: html_document
author: "Natalie Block"
date: '`r format(Sys.time(), "%B %d, %Y")`'
---
# Introduction
This dataset contains information collected from peer-reviewed autism prevalence studies. The dataset has information about the findings of these studies and also about the study design. The goal in my analysis is to see if there is a difference in autism prevalance findings based on differing study design.



```{r, loading, include = FALSE}
#load dataset
here::i_am("final_report.Rmd")
data<-readRDS(here::here("output/ASD_clean.RDS"))

#loading packages
library("gtsummary")
library("ggplot2")
```



# Tables
## Regression of Prevalence with Case Identification Type
The table shows the regression of Prevalence with Case Identification Type. Case ID type was determined to be remote if case identification occurred through mail, records, or on a registry. Case ID type was determined to be interactive if case identification occurred in-person, over the phone, or through an interview. This model shows a significant decrease in detected prevalence of ASD if identification was done remotely. In further research, the model will be fine-tuned to account for additional variables.

```{r, regression, echo = FALSE}
#creating linear model of prevalence
prevalence_model<-lm(ASD.Prevalence.Estimate.per.1.000~id_type, data=data)
summary_prevalence_model<-summary(prevalence_model)

#creating table for linear model
regression_table<-tbl_regression(prevalence_model)
regression_table %>% modify_header(label='Prevalence')
```

# Figures
## Boxplot of ASD Prevalance by Highest Age Group Represented in the Study
This box plot shows the ASD prevalence estimate per 1000 population based on the highest age category of participants for each study. Age categories were determined as follows: infant (0-1 yrs), toddler (2-3 yrs), preschool (4-5 yrs), grade school (6-12 yrs), teen (13-18 yrs), and adult (18+ yrs).

```{r, graph, echo=FALSE, fig.cap = "Estimation of ASD prevalence per 1000 population by maximum age group represented in the study"}
#creating graph of case upper age limit by prevalence
age_upper_prevalance<-ggplot(data, aes(age_upper_cat, ASD.Prevalence.Estimate.per.1.000, color=age_upper_cat))+geom_boxplot()+labs(title= "ASD Prevalance by Age Limit of Study", y="Prevelance per 1000 Population", x="Highest Age Group in Study")
print(age_upper_prevalance)
```

```